Analytic Occultation Light Curves in Reflected Light

### 2020-04-05 tex/ms.tex
better

@@

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so the
solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb). We compute this by first weighting the solution
for the occultation in emitted light by the intensity profile as in
case 3. The flux $f_3$ obtained in this fashion contains the contribution
from the entire nightside, which as we discuss above is unphysically weighted
by the negative part of Equation~(\ref{eq:illum_poly}). We can compute what
this contribution is from the complement of case 0:
%
\begin{proof}{}
    \label{eq:f0hat}
    \hat{f}_0 & =
    -\BS{\rho}^\top(-b, r_s)
    \BF{A_1}
    \BF{R}''(-x_s, -y_s)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{proof}
%
i.e., the flux we would get if we placed a negative illumination source
at the antipode $(-x_s, -y_s, -z_s)$ of the true source.
The total flux in this case is thus
%
\begin{proof}{}
    \label{eq:f4}
    f_4 = f_3 - \hat{f}_0
    \quad.
\end{proof}

@@

As in \citet{Luger2019}, the approach to computing the surface integrals
of each of the terms in $\bg$ over $S$
is to use Green's theorem to transform them into line integrals along the
curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
corresponding to the line integrals
along the curves $P$, $T$, and $Q$, respectively, for each of the terms in
$\bg$. The integration is performed in the frame $\mathcal{F}'$,
in a counter-clockwise direction relative to the center
of the integration region $S$.
Then the integral of $\bg$ over $S$ is%
\footnote{%
    The components of the vectors $\mathfrak{p}^\top$ and
    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
    $\mathcal{P}$ and $\mathcal{Q}$
    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
    integration limits of both and the sense of integration of $\mathcal{P}$
    are different.
}
%
\begin{align}
    \label{eq:sT}
    \sT & =
    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
    \quad,
\end{align}
%
where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
%
We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
%
\begin{align}
    f_S & =
    \mathfrak{s}^\top(b, \theta', b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
Note that this is not necessarily the \emph{observed} flux, which we must
compute on a case-by-case basis below.

Case 5 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 6--8 involve two points of intersection between the occultor limb and
the terminator. Case 6 corresponds to occultors that block some of the
nightside and some of the dayside, regardless of whether the occultor
is fully within the disk of the occulted body. We begin by computing the
flux over the unocculted region, $f_3$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_3 - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Case 7 corresponds to occultors that \xxx{what?}
%
\begin{proof}{}
    \label{eq:7}
    f_7 = f_3 - f_S
    \quad.
\end{proof}
%
Finally, case 8 corresponds to occultors that \xxx{what?}
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_S
    \quad.
\end{proof}
%

\subsection{Cases 9--10}
\label{sec:cases-9-10}
%
Pathological cases with 3 or 4 roots here.

>>>>

Finally, for future reference, we can also compute what we will call the
\emph{complement} of case 0:
    \label{eq:f0hat}
    \hat{f}_0 & =
    -\BS{\rho}^\top(-b, r_s)
    \BF{R}''(-x_s, -y_s)
This is the flux we would get if we placed a \emph{negative} illumination
source at the antipode $(-x_s, -y_s, -z_s)$ of the true source, and
will be useful in negating the unphysical negative contribution from our
polynomial illumination function (Equation~\ref{eq:illum_poly}) in
the following section.

@@

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve. In particular, we can use the original emitted
light solution from \citet{Luger2019}, provided we weight the map by our
polynomial illumination function:
%
\begin{proof}{}
    \label{eq:fI}
    f_I &=
    \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{proof}
%
where $\sTe(b_o, r_o)$ is the emitted light solution vector
\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
measure from a body whose surface map is weighted by the illumination function
$\BF{I}(b, \theta', r_s)$ during an occultation. Note that this is not
necessarily the \emph{observed} flux, since this may include the unphysical
negative contribution from the nightside. We must compute the actual
observed flux on a case-by-case basis.

Case 1 corresponds to any complete occultation of the body
($b_o \le r_o - 1$), so the solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside, and
we can simply use the weighted solution in emitted light
(Equation~\ref{eq:fI}):
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = f_\mathrm{I}
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb). We first compute the illumination-weighted flux
$f_I$ as above, then negate the unphysical nightside contribution
using Equation~(\ref{eq:f0hat}):
%
\begin{proof}{}
    \label{eq:f4}
    f_4 = f_I - \hat{f}_0
    \quad.
\end{proof}

@@

As in \citet{Luger2019}, the approach to computing the surface integrals
of each of the terms in $\bg$ over $S$
is to use Green's theorem to transform them into line integrals along the
curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
corresponding to the line integrals
along the curves $P$, $T$, and $Q$, respectively, for each of the terms in
$\bg$. The integration is performed in the frame $\mathcal{F}'$,
in a counter-clockwise direction relative to the center
of the integration region $S$.
Then the integral of $\bg$ over $S$ is%
\footnote{%
    The components of the vectors $\mathfrak{p}^\top$ and
    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
    $\mathcal{P}$ and $\mathcal{Q}$
    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
    integration limits of both and the sense of integration of $\mathcal{P}$
    are different.
}
%
\begin{align}
    \label{eq:sT}
    \sT & =
    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
    \quad,
\end{align}
%
where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
%
We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
%
\begin{align}
    \label{eq:fS}
    f_S & =
    \mathfrak{s}^\top(b, \theta', b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
Note again that this is not necessarily the \emph{observed} flux, which we must
compute on a case-by-case basis below.

Case 5 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 6--8 involve two points of intersection between the occultor limb and
the terminator. Case 6 corresponds to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. We begin by computing the
flux over the unocculted region, $f_3$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Cases 7 and 8 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 7
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:7}
    f_7 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 8 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_S
    \quad.
\end{proof}
%

\subsection{Cases 9--10}
\label{sec:cases-9-10}

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pathological.pdf}
        \oscaption{pathological}{%
            Two additional families of occultations in reflected light,
            involving rare triple (case 9, left) and quadruple
            (case 10, right) intersections between the limb of the
            occultor and the terminator of the occulted body. Both cases
            involve integration over two disjoint regions (bounded by
            the orange curves in the figure). The insets next to each case
            show a zoomed-in version of two such regions. See text for
            more details.
            \label{fig:pathological}
        }
    \end{centering}
\end{figure}

Pathological cases with 3 or 4 roots here (Figure~\ref{fig:pathological}).
